[Result, but poetic]: Does LLM Use Improve Data Science Education?

### 2024-07-19 paper/paper.qmd
finished some initial visualizations

---
title: "[Result, but poetic]: Does LLM Use Improve Data Science Education?"
subtitle: "Evidence from a Canadian Undergraduate Statistics Course"
author: 
  - Rohan Alexander
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/llms-achievement."
date: today
date-format: long
abstract: "Blah Blah Blah Blah"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

@@

>>>>

---
title: "[Result, but poetic]: Does LLM Use Improve Data Science Education?"
subtitle: "Evidence from a Canadian Undergraduate Statistics Course"
author: 
  - Rohan Alexander
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/llms-achievement."
date: today
date-format: long
abstract: "Blah Blah Blah Blah"
format: pdf
number-sections: true
bibliography: references.bib
nocite: |
  @*
---

```{r setup}
## Workspace Setup ##
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(knitr)
library(kableExtra)
library(lintr)

# Import data
survey_data <- read_csv("../data/analysis_data/clean_STA302_postcourse_survey_w24.csv")
```

@@

```{r fig-boilerplate}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: (CHANGE) Boilerplate figure caption 
#| fig-align: center

# survey_data |>
#   ggplot(program_counts, aes(x = "", y = n, fill = program_of_study)) +
#   #put geom type here (put before compilation) +
#   labs(title = "Title!",
#        x = "X label",
#        y = "Y label") +
#   theme_minimal() +
#   scale_fill_discrete(name="Legend Title") +
#   theme(plot.title.position = "plot",
#         plot.title = element_text(hjust = 0.5)
#         )

```

```{r tbl-boilerplate}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: (CHANGE) Boilerplate table caption 
#| fig-align: center

#Put code below this line

```

```{r fig-gpa-hist}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: Distribution of Student GPA
#| fig-align: center

#Histogram of GPA

survey_data |>
    ggplot(aes(x = gpa)) +
    geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black") +
    labs(title = "Distribution of Student GPA",
         x = "GPA",
         y = "Frequency") +
    theme_minimal() +
    theme(plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5))

```

```{r fig-year-bar}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: Distribution of Students by Year
#| fig-align: center

#Bar plot of year
survey_data |> ggplot(aes(x = year)) +
    geom_bar(fill = "skyblue", color = "black") +
    labs(title = "Distribution of Students by Year",
         x = "Year",
         y = "Frequency") +
    theme_minimal() +
    theme(plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5))

```

```{r fig-programs-pie}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: Student Self-Perception of Writing Ease
#| fig-align: center

#Pie chart of program of study

program_counts <- survey_data |> 
  count(program_of_study)

ggplot(program_counts, aes(x = "", y = n, fill = program_of_study)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  labs(title = "Distribution of Unique Programs",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  scale_fill_discrete(name="Program") +
  theme(axis.text.x = element_blank(),  # Remove x-axis text
        axis.title.x = element_blank(), # Remove x-axis title
        plot.title = element_text(hjust = 1.35)
        )

```

```{r fig-writingease-bar}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: Student Self-Perception of Writing Ease
#| fig-align: center

#Bar plot of writing ease
survey_data |> ggplot(aes(x = writing_is_easy_for_me)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Agreement to the Statement: \"Writing is Easy for Me\"",
       x = "Response",
       y = "Frequency") +
  theme_minimal() +
  theme(plot.title.position = "plot",
        plot.title = element_text(hjust = 0.5))

```
